miniKanren with fair search strategies

### 2019-05-05 Paper/paper.tex
emph sec 2

The specification that every clause in the same \conde{} is given equal 
``search priority'' is called fair \disj{}. And search strategies with 
almost-fair \disj{} give every clauss in the same \conde{} similar priority. 
Fair \conj{}, a related concept, is more complicated. We defer it to the next 
section.

@@

%\begin{figure}[tbp]
%	\begin{tabular}{|c|c|c|c|c|}
%		\hline 
%		fairness & DFS$_\textrm{i}$ & DFS$_\textrm{bi}$ & DFS$_\textrm{f}$ & 
%BFS \\ 
%		\hline 
%		disj & unfair & almost-fair & fair & fair \\ 
%		\hline 
%		conj & unfair & unfair & unfair & fair \\ 
%		\hline 
%	\end{tabular} 
%	\caption{fairness of search strategies}
%	\label{fairness}
%\end{figure}

\section{fairness}

In this section, we define fair \disj{}, almost-fair \disj{} and fair \conj{}. 
Before going further into fairness, we would like to give a short review about 
state, search space, and goal, because fairness is defined in terms of them. 
Every answer given by miniKanren corresponds to a state. Each state records a 
way how some relations can be satisfied. In our case, the state is just a 
subsitution associating logic variables with terms. In more expressive 
miniKanrens (e.g. miniKanren with with symbolic constraints 
\citep{hemann2017framework}), states can include more information. A search 
space is a collection of states. And a goal is a function from a state to a 
search space. Goals check their input states and outputs possibly extended 
states. A goal might fail for some inputs, in which case the output search 
space would be empty.

>>>>

The specification that every clause in the same \conde{} is given equal 
``search priority'' is called fair \disj{}. And search strategies with 
almost-fair \disj{} give every clauses in the same \conde{} similar priority. 
Fair \conj{}, a related concept, is more complicated. We defer it to the next 
section.

@@

\section{search strategies and fairness}

In this section, we define fair \disj{}, almost-fair \disj{} and fair \conj{}. 
Before going further into fairness, we would like to give a short review about 
state, search space, and goal, because fairness is defined in terms of them. 
Each \emph{state} records a way how some relations can be satisfied. Every 
answer given by miniKanren corresponds to a state. In our case, the state is 
just a substitution associating logic variables with terms. In more expressive 
miniKanrens (e.g. miniKanren with with symbolic constraints 
\citep{hemann2017framework}), states can include more information. A 
\emph{search space} is a collection of states. And a \emph{goal} is a function 
from a state to a search space. Goals check their input states and outputs 
possibly extended states. A goal might fail for some inputs, in which case the 
output search space would be empty.
